\documentclass{article}

\usepackage{float}
\usepackage[a4paper, margin=2cm]{geometry}

\begin{document}

% Title Page
\begin{titlepage}
    \hrule height 0.1cm
    \vspace{40pt}
    \begin{flushright}
        \Huge\textbf{Software Requirement\\Specification\\}
        \vspace{30pt}
        \Large\textbf{for\\}
        \vspace{25pt}
        \huge\textbf{Test Case\\Generator\\}
        \vspace{25pt}
        \Large\textbf{version: 0.0}
        \vspace{50pt}

        \vfill
        \begin{Large}
            \textbf{Prepared by:\\}
            Anjali Bansal\\
            Ankit Gourav\\
            Dipesh Mangrora\\
            Sourav Jaiswal\\
        \end{Large}
        \vfill
    \end{flushright}

    % Print date on which doc is generated.
    \texttt{\today}
\end{titlepage}
\pagebreak

% Page 1
\tableofcontents
\vfill

\begin{table}[H]
    \begin{flushleft}
        \Large\textbf{Revisions}
    \end{flushleft}
    \vspace{10pt}\normalsize
    \def\arraystretch{1.2}
    \centering
    \setlength{\tabcolsep}{25pt}
    \begin{tabular}{|c|c|c|c|}
        \hline
        Version & Primary Author(s) & Description of version & Date Completed\\
        \hline\hline
        0.0 & & & \\
        \hline
        & & & \\
        \hline
    \end{tabular}
\end{table}
\pagebreak

% =================================================================

\section{Introduction}
\subsection{Document Purpose}
\paragraph{}
This document is prepared in order to determine the software requirements for the
\textbf{Test Case Generator} platform. \textbf{Test Case Generator} platform is a
web-based platform for generating test cases where developers can generate test
for different algorithms and functions. The platform allows developers to generate
scalable test cases suitable for their work. This document outlines the scope,
objectives, functional and non-functional requirements of the platform, serving as
a reference for project developers and testers.

\subsection{Scope}
\paragraph{}
The scope of TestGen Pro includes the development of a web-based application and a
command-line interface (CLI) for test case generation, review, and management. The
software will be designed to support test automation and integration into CI/CD
pipelines.

\subsection{Intended Users}
\begin{itemize}
    \item Testers
    \item Developers
    \item Programmers
    \item Project Managers
    \item Technical Writers
    \item Educators and Students
    \item Open Source Contributors
    \item Test Automation Engineers
\end{itemize}

\subsection{Definitions, Acronyms, and Abbreviations}
\begin{itemize}
    \item SRS: Software Requirements Specification
    \item CI/CD: Continuous Integration/Continuous Deployment
    \item API: Application Programming Interface
    \item UI: User Interface
\end{itemize}

\subsection{Document Convention}
\paragraph{}
This Document was created based on the IEEE template for System Requirement
Specification Documents.

% =================================================================

\section{Overall Description}
\subsection{Product Perspective}
\paragraph{}
Test Generator is developed to allow coders to test their codes for different scenarios.
It reduces coder's efforts and saves their time.

\subsection{Production Functions}
\begin{itemize}
    \item The system should allow a user to select a option among various data types.
    \item The system should allow a user to give a range for result.
    \item The system should allow a user to choose result in different forms.
\end{itemize}

\subsection{Operating Environment}
\paragraph{}
PC or Laptops:
\begin{itemize}
    \item Linux (Ubuntu, Fedora, etc.)
    \item macOS
    \item Microsoft Windows (XP and above)
\end{itemize}
\paragraph{}
Cellphones, Tablets (Android or IOS), Smart TV's etc.

% =================================================================

\section{System Overview}
\subsection{System Description}
\paragraph{}
Test case generator is an all in one test case generating solution, providing a range
of features for test case creation, review, and integration. It targets software
developers, testers, quality assurance professionals, and DevOps engineers.

\subsection{System Architecture}
Test case generator adopts a client-server architecture. The web-based UI interacts with
the server to provide an interactive interface, while the CLI and APIs enable automation
and integration.

% =================================================================

\section{External Interface Requirements}
\subsection{User Interfaces}
\subsubsection{Web-Based User Interface (UI)}
\paragraph{}
\textbf{Layout and Navigation}: The UI features an intuitive layout and user-friendly navigation.
\vspace{-0.4cm}
\paragraph{}
\textbf{Interactions}: Users can create, manage, and review test cases with ease.
\vspace{-0.4cm}
\paragraph{}
\textbf{Tooltips}: Informative tooltips assist users in understanding features and functionalities.

\subsection{Command-Line Interface (CLI)}
\subsubsection{CLI Commands}
\paragraph{}
The CLI provides a set of commands mirroring the features of the UI.

\subsection{Hardware Interfaces}
\begin{itemize}
    \item Mobile devices
    \item Laptop, PCs
\end{itemize}

\subsection{Software Interfaces}
\begin{itemize}
    \item Android 5.0 and above
    \item Linux (Ubuntu, Fedora, etc.)
    \item macOS
    \item Microsoft Windows (XP and above)
\end{itemize}

\subsection{Communication Interfaces}
\paragraph{}
Requires an internet connection (Ethernet/WIFI).

% =================================================================

\section{Functional Requirements}

\subsection{User Management}
\subsubsection{User Registration and Authentication}
\paragraph{}
Users can register accounts and authenticate securely.

\subsubsection{User Roles and Permissions}
\paragraph{}
The system supports user roles (admin, tester, developer) with varying access levels.

\subsubsection{User Profile Management}
\paragraph{}
Users can update personal information and preferences.

\subsection{Test Case Generation}
\subsubsection{Customizable Parameters}
\paragraph{}
Users define test case generation parameters, including input data, constraints, and
coverage criteria.

\subsubsection{Multiple Coverage Criteria}
\paragraph{}
The software supports various coverage criteria, such as code coverage and branch coverage.

\subsubsection{Manual and Automated Generation}
\paragraph{}
Test case generation can be triggered manually or integrated into automated processes.

\subsubsection{Random and Deterministic Options}
\paragraph{}
Users can choose between random and deterministic test case generation methods.

\subsection{Test Case Review and Approval}
\subsubsection{Test Case Review}
\paragraph{}
Users can review generated test cases individually or in batches.

\subsubsection{Approval Workflow}
\paragraph{}
An approval workflow allows users to approve or reject test cases based on predefined criteria.

\subsection{Data Import and Export}
\subsubsection{Data Import}
\paragraph{}
The system supports the import of existing test data and test case templates from various
sources, including files and databases.

\subsubsection{Data Export}
\paragraph{}
Users can export generated test cases in various formats (CSV, JSON, XML).

\subsubsection{Integration with Test Management Tools}
\paragraph{}
Test case generator integrates with external test management tools through APIs.

\subsection{Integration and Automation}
\subsubsection{CI/CD Integration}
\paragraph{}
The software can be integrated into CI/CD pipelines to automate test case generation.

\subsubsection{Webhooks and Event Triggers}
\paragraph{}
Users can trigger test case generation and events through webhooks and events.

\subsection{Command-Line Interface (CLI)}
\subsubsection{Feature Parity}
\paragraph{}
The CLI provides feature parity with the web-based UI, enabling scripted and
automated test case generation tasks.

\subsection{Error Handling and Reporting}
\subsubsection{Comprehensive Error Handling}
\paragraph{}
The system handles errors gracefully and provides informative error messages to users.

\subsubsection{Logging}
\paragraph{}
Errors and system events are logged for debugging and troubleshooting.

% =================================================================

\section{Non-Functional Requirements}
\subsection{Performance}
\paragraph{}
Response times for test case generation and API requests should meet defined performance
standards. The software should support multiple concurrent users without significant
performance degradation.

\subsection{Scalability}
\paragraph{}
The system must be able to scale horizontally to accommodate increasing workloads.
It should be able to handle a growing number of users and generated test cases.

\subsection{Security}
\paragraph{}
Data transmission must be encrypted using SSL/TLS to protect sensitive information.
User authentication and authorization mechanisms should be robust and secure.
Regular security audits and vulnerability assessments should be conducted.

\subsection{Data Privacy}
\paragraph{}
The software should comply with relevant data privacy regulations (e.g., GDPR, HIPAA) if applicable.
Implement data anonymization and encryption where necessary.

\subsection{Accessibility}
\paragraph{}
The user interface must be accessible to users with disabilities and compliant with accessibility standards (e.g., WCAG).

\subsection{Reliability}
\paragraph{}
The software should be highly reliable, with minimal downtime.
Implement mechanisms for data backup and recovery in case of system failures.

\subsection{Compatibility}
\paragraph{}
Ensure compatibility with a wide range of web browsers (e.g., Chrome, Firefox, Safari, Edge).
Verify compatibility with different operating systems (e.g., Windows, macOS, Linux).

\subsection{Internationalization (i18n) and Localization (l10n)}
\paragraph{}
Support multiple languages and locales in the user interface.
Format dates, times, and numbers according to the user's locale.

\subsection{Documentation}
\paragraph{}
Provide comprehensive user and developer documentation.
Keep documentation up to date and easily accessible.

\subsection{User Support}
\paragraph{}
Offer channels for user support and feedback, such as email, chat, or a helpdesk system.
Ensure timely responses to user inquiries and issues.

\subsection{Regulatory Compliance}
\paragraph{}
Comply with industry-specific regulations and standards, where applicable (e.g., ISO 9001 for quality management).

\subsection{Usability}
\paragraph{}
The user interface should be intuitive and user-friendly.
Conduct user testing to gather feedback for usability improvements.

% =================================================================

\section{Product Convention}
\subsection{Project Naming Convention}
\paragraph{}
Choose a clear and concise name for the project, avoiding special characters or spaces.
Use camelCase or snake\_case for multi-word project names.
Example\: testCaseGenerator or test\_case\_generator

\subsection{Versioning}
\paragraph{}
Follow Semantic Versioning (SemVer) for version numbers (e.g., MAJOR.MINOR.PATCH).
Start with version 1.0.0 for the initial release.

\subsection{Coding Standards}
Follow a consistent coding style guide (e.g., PEP 8 for Python, or the appropriate
language-specific guide). Use meaningful variable and function names for improved
code readability.

\subsection{Documentation}
\paragraph{}
Provide detailed documentation for installation, usage, and maintenance.Use a
documentation generator tool (e.g., Sphinx or Doxygen) for creating user and developer
documentation.

\subsection{Testing and Test Cases}
\begin{itemize}
    \item Implement unit tests to ensure code reliability.
    \item Maintain a separate test suite or directory.
    \item Create and document sample test cases for end-users.
\end{itemize}

\subsection{Source Code Management}
\begin{itemize}
    \item Use a version control system (e.g., Git).
    \item Host the project repository on a platform like GitHub or GitLab.
    \item Adhere to a branching strategy (e.g., feature branching).
\end{itemize}

\subsection{Licensing}
\paragraph{}
Choose an appropriate open-source license (e.g., MIT, Apache License, or GPL) and
include it in your project's repository.

\subsection{Dependencies and Package Management}
Use a package manager (e.g., pip for Python) to manage project dependencies.
Include a requirements.txt file to specify required packages and their versions.
Error Handling and Logging:
\begin{itemize}
    \item Implement consistent error handling strategies.
    \item Use logging libraries for debugging and error reporting.
\end{itemize}

\subsection{Security}
\begin{itemize}
    \item Regularly update dependencies to patch known vulnerabilities.
    \item Perform security audits and code reviews periodically.
\end{itemize}

\subsection{User Interface (UI) Guidelines}
\begin{itemize}
    \item If the software includes a UI, adhere to design and usability guidelines.
    \item Ensure cross-browser and cross-platform compatibility.
\end{itemize}

\subsection{Performance Optimization}
\begin{itemize}
    \item Continuously monitor and optimize software performance.
    \item Profile code to identify and address bottlenecks.
\end{itemize}

\subsection{Release and Deployment}
\begin{itemize}
    \item Follow a deployment strategy (e.g., continuous integration/continuous
        deployment) to streamline releases.
    \item Document the release process and maintain release notes.
\end{itemize}

\subsection{User Support and Feedback}
\begin{itemize}
    \item Establish channels for user feedback and support.
    \item Respond promptly to user inquiries and issues.
\end{itemize}

\subsection{Quality Assurance}
\begin{itemize}
    \item Implement code review processes to maintain code quality.
    \item Use automated code analysis tools (e.g., linters, static analyzers) where applicable.
\end{itemize}

\subsection{Code Repository Structure}
\paragraph{}
Organize code, documentation, and related files into a structured directory layout for easy navigation.

\subsection{Contributor Guidelines}
\paragraph{}
If the project is open source, provide contribution guidelines for external contributors.

\subsection{Continuous Improvement}
\paragraph{}
Encourage continuous improvement through retrospectives and feedback loops.

\end{document}
